Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2017-03-11 Draft_1.tex
Added headings for required sections, and began work on problem definition

@@

\section{Implementation}
\label{sec:Implementation}
The application was implemented using the Python programming language, chosen for the availability of the Natural Language Toolkit (NLTK) \cite{NLTK}. NLTK provides an interface for use with Wordnet and a number of useful corpura (collections of tagged raw text), to be used as test data.

@@

>>>>

\section{Introduction}
\label{sec:Intro}

@@

\section{Problem Analysis}
\label{sec:ProbAnalysis}
Semantic analysis is the process of extracting meaning from a sentence's tokens. Each individual token in a sentence has potentially many possible meanings; an effective tool should select the correct meaning, based upon each word's surrounding context. Throughout the \hyperref[sec:PrevWork]{previous work section} of the Literature Review, it is clear that Semantic Analysis is a problem which remains unsolved.

Previously, \hyperref[sec:LSA]{statistical methods} have been used to solve this problem. These methods

It is well known that the human brain's process of semantic analysis, is very effective.

Given the following sentence:

\[The\: party\: led\: government.\]

the reader knows that "party"refers to a political party, likely, as discussed in the \hyperref[sec:DisambiguationModels]{Disambiguation Models section}, due to its pairing with the word "government".

\section{Design and Implementation}
\label{sec:Implementation}
The application was implemented using the Python programming language, chosen for the availability of the Natural Language Toolkit (NLTK) \cite{NLTK}. NLTK provides an interface for use with Wordnet and a number of useful corpura (collections of tagged raw text), to be used as test data.

@@

\section{Results and Evaluation}
\label{sec:Results}

\section{Conclusions}
\label{sec:Conclusions}
